---
title: "CATCH Q4 Meeting notes"
author: Robin Lovelace, University of Leeds
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Note: move to vignettes folder eventually
```

## Reading and cleaning data

Nikée has written an R package, **TravelAIR**, for working with the TAI data.

This function, for example, reads in the custom data format:

```{r, eval=FALSE}
readData <- function(inputPath, minObsDate="2014-01-01",
                   maxObsDate="2016-10-01",
                   saveOutput=TRUE, outputPath=inputPath,
                   saveSummary=TRUE, summaryName="Aug14-16_Summary",
                   summaryPath=inputPath)
# example usage, 1 minute to procss to process 180 MB
# system.time(readData(inputPath = "tai-private-data/")) 
```




## I/O results

<div class="columns-2">

**Original data**
```
[
  {
    "distance": 5757.0, 
    "changed_method": null, 
    "d": "190111", 
    "deleted": null, 
    "ts": 1547224631587, 
    "method_desc": "Car", 
    "duration": 312.0, 
    "to_loc": [
      -1.790163, 
      55.30009
    ], 
    "from_loc": [
      -1.831256, 
      55.34619
    ], 
    "method": 15, 
```

**The processed data**

```{r, message=FALSE}
f = paste0("tai-private-data/",
           "Base_Agent-1.csv")
d = readr::read_csv(f) # 22999 rows (trips)
head(d)
```

</div>

## Cleaning the data

Extensible function for cleaning the data:

```{r, eval=FALSE}
cleanData<-function(inputPath, inputName="Base",
                    methodSpecific=c("Car", "Bicycle"),
                    thresholdSpeed=c(rep(240,11),1200,240),
                    unrealMerge=FALSE,
                    removeMethodUnknown=FALSE,
                    outputPath=inputPath, outputName="Cleaned"){ ... }

```

## Example of data cleaning

```{r}
a = read.csv("travelAIData/BasicData/Base_Agent-101.csv")
ac = read.csv("travelAIData/BasicData/Cleaned_Agent-101.csv")
nrow(a)
nrow(ac)
summary(a$speed)
summary(ac$speed)
```

## Issue: international forrays

```{r}
plot(ac$to_locx, ac$to_locy) # viz issues
```


## Addition cleaning steps (prototype)

```{r}
a_bounds_x = quantile(ac$from_locx, probs = c(0.1, 0.9))
a_bounds_y = quantile(ac$from_locy, probs = c(0.1, 0.9))
sel_bb = ac$to_locx > a_bounds_x[1] & ac$to_locx < a_bounds_x[2]
ac = ac[sel_bb,]
plot(ac$to_locx, ac$to_locy)
```

## Visualisation

```{r}
library(leaflet.extras)
leaflet() %>% addTiles() %>% addWebGLHeatmap(ac$to_locx, ac$to_locy, size = 10000, units = "m", alphaRange = 0.00001) 
```

## Analysis of the data

- Distance to workplace estimated based on first instance when an agent is at a workplace
- Estimated purpose of trip using time-of-day (midnight to 4 AM)
- Created trip level table on commutes
- Agent-level table summarising commute behaviour
- Explored ways to define a 'typical commute' per agent. This includes:
    - Mode: single or dual mode estimated
    - Start time, end time
    - Distance (route and Euclidean)
    - Total number of commutes identified per agent (suggest below 5 - is not reliable)
    
## Identification of aggregate patterns in commute behaviour

- Based on input data, females commute on average 7.9 km to home and 5.1 to work (intermediate stops on the way home?)
- For men the route distances values are 17.8 and 17.5 km, respectively
- Estimated travel times but these do not seem reliable
- Breakdown by age band

## Some results I | Main mode of commute by age band

```{r, message=FALSE, warning=FALSE}
knitr::kable(readr::read_csv("vignettes/results-age-mode.csv"))
```

## Some results II | Main mode of commute by age band

```{r, message=FALSE, warning=FALSE}
knitr::kable(readr::read_csv("vignettes/results-gender-mode.csv"))
```
