---
title: "Q4 meeting notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading and cleaning data

Nikee has written an R package for working with the TAI data.

This function for example, reads in the custom data format:

```{r, eval=FALSE}
readData<-function(inputPath, minObsDate="2014-01-01", maxObsDate="2016-10-01",
                   saveOutput=TRUE, outputPath=inputPath,
                   saveSummary=TRUE, summaryName="Aug14-16_Summary", summaryPath=inputPath)
```

## Analysis of the data


- Distance to workplace estimated based on first instance when an agent is at a workplace
- Estimated purpose of trip using time-of-day (midnight to 4 AM)
- Created trip level table on commutes
- Agent-level table summarising commute behaviour
- Explored ways to define a 'typical commute' per agent. This includes:
    - Mode: single or dual mode estimated
    - Start time, end time
    - Distance (route and Euclidean)
    - Total number of commutes identified per agent (suggest below 5 - is not reliable)

## Identification of aggregate patterns in commute behaviour

- Based on input data, females commute on average 7.9 km to home and 5.1 to work (intermediate stops on the way home?)
- For men the route distances values are 17.8 and 17.5 km, respectively
- Estimated travel times but these do not seem reliable
- Breakdown by age band


